### 2023-05-09 main.tex
ll
s
ii

Thus the explicit expression becomes
\begin{equation}
G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},\ldots,k_{N}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+\cdots+k_{3})})\right)
\end{equation}
with the same notation as in $N=3$ case. 
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
		\\&
		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
	\end{split}
\end{equation}
We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
\begin{equation}
	\begin{split}
	A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
	A_{3}=\left\{\left((2x+N)(\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
Therefore we rewrite \eqref{cond4} as 
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
The left-hand-side is 
\begin{equation}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\end{equation}
while, on the right-hand-side we have
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&=
\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\end{split}
\end{equation}
and similarly 
\begin{equation}
	\begin{split}
		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		\\&=
		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
	\end{split}
\end{equation}
Therefore,
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&+
	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
	\end{split}
\end{equation}
Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.

@@

A_{j}=	\left\{\left((\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}

@@

We observe that $\forall i,j=1,2,\ldots,N$
\begin{equation}
	\sum_{a,b=1}^{L}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
\end{equation}
then 
\begin{equation}
	\boxed{A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}}
\end{equation}
{\color{blue}ok}

@@

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
	\end{split}
\end{equation}
{\color{blue}ok}
%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)}
\end{split}
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}{\color{red}=N}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}2+2N}\\
	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
\begin{split}
Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
\end{split}
\end{equation}
it has the property that commute with the equilibrium Hamiltonian.

All terms are diagonal except the last one which can  be  identified with the second Casimir of the $gl(N-1)$ subalgebra
\begin{equation}
\hat C_2^{N-1} \sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
\end{equation} 
On the Bethe states (and on the irrep decomposition of the spin chain) it acts diagonally with eigenvalues given in terms of shifted weights 
\begin{equation}
 C_2^{N-1}=\sum\prod\frac{1}{\ell-\ell}
\end{equation} 
Thus the eigenvalues of the transfer matrix can be writen as 
\begin{equation}
\begin{split}
 \Lambda(x)&= \Lambda_{2L+2} x^{2L+2}+ \Lambda_{2L+1} x^{2L+1}+ \Lambda_{2L}x^{2L}+\ldots
 \\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)\sum_{j=2}^{N}m_j+2C_{2}^{N-1}\right)x^{2L}+\ldots
 \end{split}
\end{equation} 
{\color{blue}Do we have $
 \sum_{i=1}^N m_i=L$?
}
Thus the difference is of order $2L$ and becomes
\begin{equation}
 \Lambda(x)-T_0(x)=x^{2L}\left(\Lambda_{2L}-Q_{2L}^0\right)+\ldots
\end{equation} 
We can take the limit
\begin{equation}
 \lim_{x\to\infty}\frac{2x+N}{\Lambda(x)-T_0(x)}B_{i}(x)=\frac{2}{\Lambda_{2L}-Q_{2L}^0}B_i^{2L-1}
\end{equation} 
{\color{blue}ok?}

@@

>>>>

Thus the explicit expression becomes
\begin{equation}
G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},\ldots,k_{N}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+\cdots+k_{3})})\right)
\end{equation}
with the same notation as in $N=3$ case. 
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
		\\&
		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
	\end{split}
\end{equation}
We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
\begin{equation}
	\begin{split}
	A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
	A_{3}=\left\{\left(2x+N)((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
Therefore we rewrite \eqref{cond4} as 
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
The left-hand-side is 
\begin{equation}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\end{equation}
while, on the right-hand-side we have
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&=
\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\end{split}
\end{equation}
and similarly 
\begin{equation}
	\begin{split}
		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		\\&=
		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
	\end{split}
\end{equation}
Therefore,
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&+
	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
	\end{split}
\end{equation}
Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.

@@

A_{j}=	\left\{\left((2x+N)(\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}

@@

We observe that $\forall i,j=1,2,\ldots,N$
\begin{equation}
	\sum_{a,b=1}^{L}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
\end{equation}
then 
\begin{equation}
	\boxed{A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}}=2e_{11}^{tot}\left(e_{11}^{tot}+I^{tot}\right)-L
\end{equation}
{\color{blue}ok?}

@@

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}=	2Ne_{ii}^{tot}+ 2e_{11}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
	\end{split}
\end{equation}
{\color{blue}ok?}
%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)}
\end{split}
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}{\color{red}=N}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}2+2N}\\
	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
\begin{split}
Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
&=N+2e_{11}^{tot}(e_{11}^{tot}+1)-(N+2)(L-e_{11}^{tot})+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
\end{split}
\end{equation}
where we used $
 \sum_{i=1}^N m_i=L$.

%  It has the property that commute with the equilibrium Hamiltonian.

All terms are diagonal except the last one which can  be  identified with the second Casimir of the $gl(N-1)$ subalgebra
\begin{equation}
\hat C_2^{N-1}= \sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
\end{equation} 
On the Bethe states (and on the irrep decomposition of the spin chain) it acts diagonally with eigenvalues given in terms of shifted weights 
\begin{equation}
 C_2^{N-1}=\sum_{j=1}^{N-1}\ell_j(\ell_j -N+2)+\frac{1}{6}(N-1)(N-2)(N-3)
\end{equation} 
{\color{blue}to be checked}, see e.g. [Das,Okubo].
Thus the eigenvalues of the transfer matrix can be writen as 
\begin{equation}
\begin{split}
 \Lambda(x)&= \Lambda_{2L+2} x^{2L+2}+ \Lambda_{2L+1} x^{2L+1}+ \Lambda_{2L}x^{2L}+\ldots
 \\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)(L-m_1)+2C_{2}^{N-1}\right)x^{2L}+\ldots
 \end{split}
\end{equation}

Thus the difference is of order $2L$ and becomes
\begin{equation}
 \Lambda(x)-T_0(x)=x^{2L}\left(\Lambda_{2L}-Q_{2L}^0\right)+\ldots
\end{equation} 
We can take the limit
\begin{equation}
 \lim_{x\to\infty}\frac{2x+N}{\Lambda(x)-T_0(x)}B_{i}(x)=\frac{2}{\Lambda_{2L}-Q_{2L}^0}B_i^{2L-1}
\end{equation} 
{\color{blue}ok?}

@@

{\color{blue}Adopt notation here}
